Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa

### 2022-07-11 src/docs_paper/paper.Rmd
Add author contributions #128

>>>>

## Author contributions

* Conceptualisation: JWE, KAR, CB
* Data curation: AH, KAR, VKN, RE, OS, JWE
* Formal analysis: AH
* Funding acquisition: JWE
* Investigation: AH
* Methodology: AH, KAR, VKN, TMW, SRF, JWE
* Project administration: JWE, KAR, CB
* Software: AH, KAR
* Supervision: JWE, SRF
* Visualisation: AH
* Writing - Original draft: AH
* Writing - Review and Editing: AH, KAR, VKN, OS, KMJ, RE, LZ, IW, MM, CB, SRF, JWE
